\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-09-19 draft.tex
revise gov't structure in sec:basic (except extensive form)

\textbf{REVISE GOVERNMENT STRUCTURE}

In each country, there is an executive who concludes trade agreements and a legislature that has final say on trade policy. To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, I assume that only the import-competing industry in each country is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies. To illustrate, adding an export lobby with no uncertainty predicts import lobbies remain disengaged while the executives can reduce tariffs by recruiting support from exporters. The Panama Trade Promotion Act follows this pattern, with virtually no lobbying against, significant lobbying in favor, and numerous industries receiving import protection.\label{fn:lobby}}

@@

Figure~\ref{fig:ext} illustrates the timing of the game from the perspective of the home country.\footnote{This extensive form is for the case where the foreign legislature does not break the trade agreement.} First, the executives set trade policy cooperatively within the context of an international agreement by choosing the trade agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$.\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} Then the lobbies attempt to persuade the legislators in their respective countries to break the trade agreement by choice of lobbying effort $e_b$. Next, nature determines with probabilities $o$ and $o^*$ whether each legislature will have the opportunity to take a vote to break the agreement. I assume that these probabilities are less than one-half and mutually exclusive.\footnote{While this assumption is made for purposes of exposition and tractability, one can think of $o$ and $o^*$ as being determined by events beyond the executives' or legislatures' control that determine whether or not the legislatures will be willing to consider the lobby's request; for example, they would be affected by the occurrence of an economic crisis that diverts the legislature's attention from less-pressing matters.} This allows me to focus on the key interaction between the domestic actors and abstract from the strategic interaction between the lobbies.\footnote{If the break decisions in the two countries are sequential with the executives behind a veil of ignorance about which legislature moves first, the end results are the same but additional intermediate results are needed. The optimization problem of the executives becomes more complex as they decide how best to exploit the second lobby's incentive to free ride on the effort of the first-mover lobby.}

After this, uncertainty about the the median legislator's identity is resolved. All players simultaneously observe the realization of the random variable $\ta_b$ that represents this uncertainty. The ``break stage'' concludes with the legislature making a choice to abide by the agreement or to break the agreement. In the event that the legislature breaks the agreement, there is a final stage of lobbying, resolution of the uncertainty surrounding this decision, and voting to set the trade-war tariffs $\btn$.\footnote{Alternatively, one can model the non-cooperative tariff as being determined by the break decision lobbying, through a separate process in the case of administered protection, or the ex-ante status quo. This does not change the fundamental dynamics of the model.} Finally, producers and consumers make their decisions.

>>>>

In the home country, there is a government agency that has the power to renew (or not) anti-dumping duties. To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, we assume that only the import-competing industry is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies.\label{fn:lobby}} Policy-makers and lobbyists in the foreign country are assumed to be passive.

\textbf{REVISE EXTENSIVE FORM}

@@

Figure~\ref{fig:ext} illustrates the timing of the game. Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\bta = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.

After this, uncertainty about the government agency's preferences is resolved. All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty. The political stage concludes with the agency making a choice to renew the anti-dumping duties or let them expire. In the event that the anti-dumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$. Finally, producers and consumers make their decisions.
